Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-18 paper/manuscript.Rmd
swim-bo-baggins

In total, 12 of 29 collared female caribou swam between islands in the Fogo
archipelago. Only `r n10` of these 12 individuals had more than 10 swimming
events, suggesting that for ~10% of narjed individuals swimming is relatively
common, on average occurring approximately every `r indMean` days during
ice-free seasons. We did not detect any swimming events for the remaining 17
individuals. It remains unclear whether these individuals do not swim, or
whether swimming is rare for most caribou. Overall, there appears to be three
groups of individuals: those that swim often (~`r indMean` days), those that
swim occasionally (~`r ind2Mean` days), and those that never swam. We are also
unable to draw conclusions about the prevalence of swimming in the ocean by male
caribou: our initial visual observation was of an adult male, but our GPS data
only included females.

>>>>

In total, 12 of 29 collared female caribou swam between islands in the Fogo
archipelago. Only `r n10` of these 12 individuals had more than 10 swimming
events, suggesting that for ~10% of narjed individuals swimming is relatively
common, on average occurring approximately every `r indMean` days during
ice-free seasons. We did not detect any swimming events for the remaining 17
individuals. It remains unclear whether these individuals do not swim, or
whether swimming is rare for most caribou. Overall, there appears to be three
groups of individuals: those that swim often (n = 3, every ~`r indMean` days), those that
swim occasionally (n = 9, every ~`r ind2Mean` days), and those that never swam (n = 17). We are also
unable to draw conclusions about the prevalence of swimming in the ocean by male
caribou: our initial visual observation was of an adult male, but our GPS data
only included females.
